Appendix to "Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2023-07-07 src/docs_paper/appendix.Rmd
Add rho_a plot to appendix

>>>>

```{r rho_a, fig.cap="Variation between units can be explained either by high correlation and high variance, or by low correlation and low variance. As such, some hyperparameters has correlated posteriors. It is this correlation which is made use of by PCA-AGHQ."}
knitr::include_graphics("depends/rho_a.png")
```
